---
title: "MetaAnalysis_Updated"
author: "Amanda, Christian, & Grace"
date: "2023-11-15"
output: pdf_document
---


```{r Load in packages}
library(fsn)
library(ggplot2)
library(readr)
library(meta)
library(psych)
library(ggplot2)
library(lme4)
library(readxl)
library(excel.link)
library(tidyverse)
library(tidyr)
library(dplyr)
library(extrafont)
library(metafor)
library(readxl)

```


```{r Meta 3 Variables}

# Read the Excel file

testmeta <- read_excel("CE-language-meta-data.xlsx")

# Checking the unique combinations
unique_combinations <- unique(with(testmeta, paste(`IJA/RJA`, `Comp/Prod`, `Concurrent/Longitudinal`, sep = ": ")))

# Creating Group_all with correct levels
testmeta$Group_all <- with(testmeta, factor(paste(`IJA/RJA`, `Comp/Prod`, `Concurrent/Longitudinal`, sep = ": "),
                                  levels = unique_combinations))

# Update group_identifiers based on the actual levels found
group_identifiers_all <- setNames(seq_along(unique_combinations), unique_combinations)

# Adding the Groupn_all column
testmeta <- testmeta %>%
  mutate(Groupn_all = group_identifiers_all[as.character(Group_all)])

# Remove rows with "NA" in the Group_all column
testmeta <- testmeta %>%
  filter(!grepl("NA", as.character(Group_all)))

testmeta <- testmeta %>%
  filter(`ESCS Y/N` == "Y")

# Adding the gid_all 
testmeta$gid_all <- ave(testmeta$Groupn_all, testmeta$Groupn_all, FUN = cumsum)

# Calculate effect sizes and variances
dat_0 <- escalc(measure="MD", yi=z, vi=vi, data=testmeta, slab=paste("Group", Group_all, "gid", gid_all))

# Aggregate the data by Group_all
agg_data <- dat_0 %>%
  group_by(Group_all) %>%
  summarise(
    yi = weighted.mean(yi, w = 1 / vi),
    vi = 1 / sum(1 / vi),
    .groups = 'drop'
  )

# Calculate the sum of all weights
agg_data <- mutate(agg_data, weight = 1 / vi)

total_weight <- sum(agg_data$weight)

# Calculate the percentage weight for each study
agg_data <- mutate(agg_data, percent_weight = (weight / total_weight) * 100)

# Run the meta-analysis on the aggregated data
meta_analysis0 <- rma(yi, vi, data=agg_data, method="REML")

# Generate the forest plot
#png("/Users/cmj39767/Desktop/forestplot_all.png", width=800, height=600)

# Set up margins 
par(mar=c(5,4,4,8)) 

# Create the forest plot with the aggregated data
forest_all <- forest(meta_analysis0, refline=0, xlim=c(-1, 1), alim=c(-.4, .4), 
       cex=.9, header=TRUE, xlab="Effect Size", 
       slab=agg_data$Group_all, mlab="")
forest_all
usr <- par("usr")

# Add the percentage weight labels to the forest plot
text(x = usr[2] + 0.03 * (usr[2] - usr[1]), y = 1:nrow(agg_data), 
     labels=paste0(round(agg_data$percent_weight, 1), "%"), pos=4, xpd=TRUE, cex=.9)

# Cover the "Study" label with a white rectangle
rect(xleft=usr[1]  - 0.01 * (usr[2] - usr[1]), ybottom=par("usr")[4] - 2.2, 
     xright=usr[1] + 0.5 * (usr[2] - usr[1]), ytop=par("usr")[4], 
     col = "white", border = "white", xpd = NA)

# Add the "Group" header where "Study" was
mtext("Group", side=3, line=-.9, at=usr[1], cex=.9, font=2, las=0, adj=0, xpd=TRUE)

# Add a column header for weights 
mtext("Weights", side=3, line=-.9, at=usr[2] + .25, cex=.9, font=2, las=0, adj=1, xpd=TRUE)

```

```{r significance tests for vocabulary measures used}
Meta_data_vocab <- testmeta %>%
  select(Vocab_Measure, r)
t.test(Meta_data_RDL$r, Meta_data_CDI$r)

library(report)
report(aov(r ~ Vocab_Measure,
  data = Meta_data_vocab
))

oneway.test(r ~ Vocab_Measure,
  data = Meta_data_vocab,
  var.equal = FALSE # assuming unequal variances
)
```


```{r Forest Plot: Comparing Pooled Concurrent & Longitudinal Effect Sizes by ESCS Group }

# Filter out unwanted rows
testmeta <- testmeta[testmeta$`IJA/RJA` != "" & !is.na(testmeta$`IJA/RJA`), ]

# Combine the two columns to create the Group factor
testmeta$Group <- with(testmeta, factor(paste(`IJA/RJA`, `Concurrent/Longitudinal`, sep = ": "),
                                        levels = c( "GP: Longitudinal", "GP: Concurrent", 
                                                     "IJA: Concurrent", "IJA: Longitudinal", "RJA: Concurrent",
                                                   "RJA: Longitudinal")))

testmeta <- testmeta %>%
  filter(`ESCS Y/N` == "Y")

# Calculate effect sizes and variances
dat <- escalc(measure="MD", yi=z, vi=vi, data=testmeta, slab=paste("Group", Group, "gid", gid))

# Split data by Group
split_data <- split(dat, dat$Group)

# Function to aggregate data
aggregate_fun <- function(df) {
  yi_mean <- weighted.mean(df$yi, w = 1 / df$vi)
  vi_inv_sum <- sum(1 / df$vi)
  weight <- 1 / vi_inv_sum
  return(data.frame(yi = yi_mean, vi = 1 / vi_inv_sum, weight = weight))
}

# Apply the function 
agg_data <- do.call(rbind, lapply(split_data, aggregate_fun))
agg_data$Group <- rownames(agg_data)

# Calculate the sum of all weights
total_weight <- sum(agg_data$weight)

# Calculate the percentage weight for each study
agg_data$percent_weight <- (agg_data$weight / total_weight) * 100

# Run the meta-analysis on the aggregated data
meta_analysis_agg <- rma(yi, vi, data=agg_data, method="REML")

# Generate the forest plot
#png("~/Desktop/forestplot_CL.png", width=800, height=600)

# Set up margins 
par(mar=c(5,4,4,8)) 

# Create the forest plot
forest <- forest(meta_analysis_agg, refline=0, xlim=c(-1, 1), alim=c(-.4, .4), 
       cex=1, header=TRUE, xlab="Effect Size", 
       slab=agg_data$Group)
forest

usr <- par("usr")

text(x = usr[2] + 0.03 * (usr[2] - usr[1]), y = 1:nrow(agg_data), 
     labels=paste0(round(agg_data$percent_weight, 1), "%"), pos=4, xpd=TRUE, cex=1)

# Cover the "Study" label with a rectangle
rect(xleft=usr[1]  - 0.01 * (usr[2] - usr[1]), ybottom=par("usr")[4] - 2.2, 
     xright=usr[1] + 0.5 * (usr[2] - usr[1]), ytop=par("usr")[4], 
     col = "white", border = "white", xpd = NA)

# Add the "Group" header 
mtext("Group", side=3, line=-1.3, at=usr[1], cex=1, font=2, las=0, adj=0, xpd=TRUE)

# Add a column header for weights 
mtext("Weights", side=3, line=-1.3, at=usr[2] + .3, cex=1, font=2, las=0, adj=1, xpd=TRUE)



```

```{r Forest Plot: Comparing Pooled Productive/Comprehensive Vocabulary Effect by ESCS Group }

# Create the Group_Vocab factor with the specified levels
testmeta$Group_Vocab <- with(testmeta, factor(paste(`IJA/RJA`, `Comp/Prod`, sep = ": "),
                                              levels = c("GP: Prod", "GP: Comp", "IJA: Comp", "IJA: Prod", "RJA: Comp", "RJA: Prod")))

# Assign numeric identifiers based on the levels
group_identifiers <- c("GP: Prod" = 1, "GP: Comp" = 2, "IJA: Comp" = 3, "IJA: Prod" = 4, "RJA: Comp" = 5, "RJA: Prod" = 6)

# Filter out entries where `ESCS Y/N` is "Y"
testmeta <- testmeta %>%
  filter(`ESCS Y/N` == "Y")

# Assign numeric group identifiers
testmeta$Groupn_Vocab <- group_identifiers[as.character(testmeta$Group_Vocab)]

# Add a cumulative count within each group
testmeta$gid_vocab <- ave(testmeta$Groupn_Vocab, testmeta$Groupn_Vocab, FUN = cumsum)

# Calculate effect sizes and variances
dat_2 <- escalc(measure="MD", yi=z, vi=vi, data=testmeta, slab=paste("Group", Group_Vocab, "gid", gid_vocab))

# Aggregate the data by Group_Vocab
agg_data_2 <- dat_2 %>%
  group_by(Group_Vocab) %>%
  summarise(
    yi = weighted.mean(yi, w = 1 / vi),
    vi = 1 / sum(1 / vi),
    .groups = 'drop'
  )

# Calculate the sum of all weights
agg_data_2$weight <- 1 / agg_data_2$vi
total_weight_2 <- sum(agg_data_2$weight)

# Calculate the percentage weight for each group
agg_data_2$percent_weight <- (agg_data_2$weight / total_weight_2) * 100

# Run the meta-analysis
meta_analysis2 <- rma(yi, vi, data=agg_data_2, method="REML")


# Set up margins 
par(mar=c(5,4,4,8)) 

# Create the forest plot with the aggregated data
forest1 <- forest(meta_analysis2, refline=0, xlim=c(-1, 1), alim=c(-.4, .4), 
       cex=1, header=TRUE, xlab="Effect Size", 
       slab=agg_data_2$Group_Vocab)
forest1

usr <- par("usr")

# Add the percentage weight labels to the forest plot
text(x = usr[2] + 0.03 * (usr[2] - usr[1]), y = 1:nrow(agg_data_2), 
     labels=paste0(round(agg_data_2$percent_weight, 1), "%"), pos=4, xpd=TRUE, cex=1)

# Cover the "Study" label with a white rectangle
rect(xleft=usr[1] - 0.01 * (usr[2] - usr[1]), ybottom=par("usr")[4] - 2.0, 
     xright=usr[1] + 0.1 * (usr[2] - usr[1]), ytop=par("usr")[4], 
     col = "white", border = "white", xpd = NA)

# Add the "Group" header where "Study" was
mtext("Group", side=3, line=-1.5, at=usr[1], cex=1, font=2, las=0, adj=0, xpd=TRUE)

# Add a column header for weights 
mtext("Weights", side=3, line=-1.5, at=usr[2] + .3, cex=1, font=2, las=0, adj=1, xpd=TRUE)


```

```{r Forest Plot: Comparing Pooled Reported Effect Sizes by Age Group of JA Variable Measurement }

testmeta <- xl.read.file("CE-language-meta-data.xlsx")

# Filter for longitudinal studies
testmeta <- testmeta %>% 
  filter(`Concurrent/Longitudinal` == "Longitudinal")

# Create age1_groups based on the Age1 (months) - JA? column
testmeta$age1_groups <- cut(testmeta$`Age1 (months) - JA?`,
                             breaks = c(-Inf, 8, 11, 15, 19, 23, Inf),
                             labels = c("<8", "8-11", "11-15", "15-19", "19-23", ">23"),
                             right = FALSE)

# Create numeric identifiers for age groups
group_age_identifiers <- c("<8" = 1, "8-11" = 2, "11-15" = 3, "15-19" = 4, "19-23" = 5, ">23" = 6)

# Assign numeric group identifiers
testmeta$age1_groupn <- group_age_identifiers[as.character(testmeta$age1_groups)]

# Add a cumulative count within each age group
testmeta$gid_age1 <- ave(testmeta$age1_groupn, testmeta$age1_groupn, FUN = cumsum)

# Calculate effect sizes and variances
dat_3 <- escalc(measure="MD", yi=z, vi=vi, data=testmeta, slab=paste("Group", age1_groups, "gid", gid_age1))

# Aggregate the data by age1_groups
agg_data_3 <- dat_3 %>%
  group_by(age1_groups) %>%
  summarise(
    yi = weighted.mean(yi, w = 1 / vi),
    vi = 1 / sum(1 / vi),
    .groups = 'drop'
  )
agg_data_3 <- na.omit(agg_data_3)
# Calculate the sum of all weights
agg_data_3$weight <- 1 / agg_data_3$vi
total_weight_3 <- sum(agg_data_3$weight)

# Calculate the percentage weight for each group
agg_data_3$percent_weight <- (agg_data_3$weight / total_weight_3) * 100

# Run the meta-analysis
meta_analysis3 <- rma(yi, vi, data=agg_data_3, method="REML")

# Set up margins 
par(mar=c(5,4,4,8)) 

# Create the forest plot with the aggregated data
forest_age <- forest(meta_analysis3, refline=0, xlim=c(-1, 1), alim=c(-.4, .4), header=TRUE, xlab="Effect Size", 
       slab=agg_data_3$age1_groups, mlab="")
forest_age

usr <- par("usr")

# Add the percentage weight labels to the forest plot
text(x = usr[2] + 0.05 * (usr[2] - usr[1]), y = 1:nrow(agg_data_3), 
     labels=paste0(round(agg_data_3$percent_weight, 1), "%"), pos=4, xpd=TRUE)

# Cover the "Study" label with a white rectangle
rect(xleft=usr[1] - 0.01 * (usr[2] - usr[1]), ybottom=par("usr")[4] - 2.0, 
     xright=usr[1] + 0.1 * (usr[2] - usr[1]), ytop=par("usr")[4], 
     col = "white", border = "white", xpd = NA)

# Add the "Group" header where "Study" was
mtext("Group", side=3, line=-1.4, at=usr[1], cex=1, font=2, las=0, adj=0, xpd=TRUE)

# Add a column header for weights 
mtext("Weights", side=3, line=-1.4, at=usr[2] + .3, cex=1, font=2, las=0, adj=1, xpd=TRUE)


```



```{r Forest Plot: Pooled results for comprehensive vocabulary only  }

# Create the necessary columns
testmeta$age_category <- ifelse(testmeta$`Age2 (months) - vocab?` < 13, "young", "old")
testmeta$gaze_escs_category <- ifelse(testmeta$`ESCS Y/N` == "Y", "ESCS", "Gaze")
testmeta$age_Gaze_ESCS <- paste(testmeta$age_category, testmeta$gaze_escs_category)
testmeta$age_Gaze_ESCS_comp <- ifelse(testmeta$`Comp/Prod` == "Comp", testmeta$age_Gaze_ESCS, NA)

# Numeric identifiers for the new groups
group_ageVocab_identifiers <- c("NA Gaze" = 1, "old ESCS" = 2, "old Gaze" = 3, "young ESCS" = 4, "young Gaze" = 5)

# Add numeric group identifiers
testmeta <- testmeta %>%
  mutate(Groupn_ageVocab_type = group_ageVocab_identifiers[as.character(age_Gaze_ESCS_comp)])

# Cumulative count within each group
testmeta$gid_ageVocab <- ave(testmeta$Groupn_ageVocab_type, testmeta$Groupn_ageVocab_type, FUN = cumsum)

dat_4 <- escalc(measure="MD", yi=z, vi=vi, data=testmeta, slab=paste("Group", age_Gaze_ESCS_comp, "gid", gid_ageVocab))

# Filter out the NAs
temp_dat_4 <- dat_4[!is.na(dat_4$age_Gaze_ESCS_comp), ]

# Aggregate the data by age_Gaze_ESCS_comp
agg_data_4 <- temp_dat_4 %>%
  group_by(age_Gaze_ESCS_comp) %>%
  summarise(
    yi = weighted.mean(yi, w = 1 / vi),
    vi = 1 / sum(1 / vi),
    .groups = 'drop'
  )

# Calculate weights and percentage 
agg_data_4 <- mutate(agg_data_4, weight = 1 / vi, percent_weight = (weight / sum(weight)) * 100)

# Run the meta-analysis 
meta_analysis4 <- rma(yi, vi, data=agg_data_4, method="REML")

# Generate the forest plot
par(mar=c(5,4,4,8))  # Set up margins 

forest_oldyoung <- forest(meta_analysis4, refline=0, xlim=c(-1, 1), alim=c(-.4, .4), 
       header=TRUE, xlab="Effect Size", 
       slab=agg_data_4$age_Gaze_ESCS_comp, mlab="")
forest_oldyoung
# Add the percentage weight labels to the forest plot
usr <- par("usr")
text(x = usr[2] + 0.05 * (usr[2] - usr[1]), y = 1:nrow(agg_data_4), 
     labels=paste0(round(agg_data_4$percent_weight, 1), "%"), pos=4, xpd=TRUE)

# Cover the "Study" label with a white rectangle
rect(xleft=usr[1] - 0.01 * (usr[2] - usr[1]), ybottom=par("usr")[4] - 2.0, 
     xright=usr[1] + 0.1 * (usr[2] - usr[1]), ytop=par("usr")[4], 
     col = "white", border = "white", xpd = NA)

# Add the "Group" header where "Study" was
mtext("Group", side=3, line=-1.85, at=usr[1], cex=1, font=2, las=0, adj=0, xpd=TRUE)

# Add a column header for weights 
mtext("Weights", side=3, line=-1.85, at=usr[2] + .3, cex=1, font=2, las=0, adj=1, xpd=TRUE)



```

```{r Forest Plot: Pooled Results Comparing Old/Young Groups for all Vocabulary Types}

# Create the necessary columns
testmeta$age_category <- ifelse(testmeta$`Age2 (months) - vocab?` < 13, "young", "old")
testmeta$gaze_escs_category <- ifelse(testmeta$`ESCS Y/N` == "Y", "ESCS", "Gaze")
testmeta$age_Gaze_ESCS <- paste(testmeta$age_category, testmeta$gaze_escs_category)

# Numeric identifiers for the new groups
group_ageVocab_identifiers <- c("NA Gaze" = 1, "old ESCS" = 2, "old Gaze" = 3, "young ESCS" = 4, "young Gaze" = 5)

# Assign numeric group identifiers
testmeta <- testmeta %>%
  mutate(Groupn_ageVocab_all = group_ageVocab_identifiers[as.character(age_Gaze_ESCS)])

# Cumulative count within each group
testmeta$gid_ageVocab_all <- ave(testmeta$Groupn_ageVocab_all, testmeta$Groupn_ageVocab_all, FUN = cumsum)

# Calculate effect sizes and variances
dat_5 <- escalc(measure="MD", yi=z, vi=vi, data=testmeta, slab=paste("Group", age_Gaze_ESCS, "gid", gid_ageVocab_all))

# Aggregate the data by age_Gaze_ESCS
agg_data_5 <- dat_5 %>%
  group_by(age_Gaze_ESCS) %>%
  summarise(
    yi = weighted.mean(yi, w = 1 / vi),
    vi = 1 / sum(1 / vi),
    .groups = 'drop'
  )

# Calculate weights and percentage 
agg_data_5 <- mutate(agg_data_5, weight = 1 / vi, percent_weight = (weight / sum(weight)) * 100)

# Run the meta-analysis 
meta_analysis5 <- rma(yi, vi, data=agg_data_5, method="REML")

# Generate the forest plot

par(mar=c(5,4,4,8)) 

forest(meta_analysis5, refline=0, xlim=c(-1, 1), alim=c(-.4, .4), 
       header=TRUE, xlab="Effect Size", 
       slab=agg_data_5$age_Gaze_ESCS, mlab="")

# Add the percentage weight
usr <- par("usr")
text(x = usr[2] + 0.05 * (usr[2] - usr[1]), y = 1:nrow(agg_data_5), 
     labels=paste0(round(agg_data_5$percent_weight, 1), "%"), pos=4, xpd=TRUE)

# Cover the "Study" label with a white rectangle
rect(xleft=usr[1] - 0.01 * (usr[2] - usr[1]), ybottom=par("usr")[4] - 2.0, 
     xright=usr[1] + 0.1 * (usr[2] - usr[1]), ytop=par("usr")[4], 
     col = "white", border = "white", xpd = NA)

# Add the "Group" header where "Study" was
mtext("Group", side=3, line=-1.85, at=usr[1], cex=1, font=2, las=0, adj=0, xpd=TRUE)

# Add a column header for weights 
mtext("Weights", side=3, line=-1.85, at=usr[2] + .3, cex=1, font=2, las=0, adj=1, xpd=TRUE)

```

```{r publication bias}

#Rosenthal's fail safe:
fsn(testmeta$r, vi=testmeta$Variance, alpha = 0.01, type="Rosenthal")

#Meta-regressions of publication status

meta_pubbias <- rma(yi = testmeta$r, 
                     vi = testmeta$Variance, 
                     mods = ~ Published, 
                     data = testmeta)
meta_pubbias

testmeta_prod <- testmeta%>%
  filter(`Comp/Prod` == "Prod")

testmeta_pub <- testmeta%>%
  filter(Published == "Y")


meta_pubbias <- rma(yi = r, 
                     sei = se, 
                     mods = ~ `Concurrent/Longitudinal`-1, 
                     data = testmeta_prod)
meta_pubbias

meta_pubbias <- rma(yi = r, 
                     sei = se, 
                     mods = ~ `ESCS Y/N`-1, 
                     data = testmeta_pub)
meta_pubbias
```
```


```{r Funnel Plot: All Effect Sizes }
testmeta<- testmeta %>%
  filter(Variance > 0)



meta_analysis_EffectSize <- rma(yi = testmeta$z, 
                     vi = testmeta$Variance, 
                     data = testmeta)


funnel(meta_analysis_EffectSize, back = "white", pch = 21)

#Egger's test
regtest(meta_analysis_EffectSize)

```

```{r Funnel Plot: All ESCS Group Effect Sizes }

testmeta_escs<- testmeta %>%
  filter(`ESCS Y/N` == "Y")



meta_analysis_EffectSize <- rma(yi = testmeta_escs$z, 
                     vi = testmeta_escs$Variance, 
                     data = testmeta_escs)


funnel(meta_analysis_EffectSize, back = "white", pch = 21)

regtest(meta_analysis_EffectSize)


```

```{r Funnel Plot: All Gaze Pattern Group Effect Sizes }

testmeta_GP <- testmeta %>%
  filter(`IJA/RJA` =="GP")

meta_analysis_EffectSize_GP <- rma(yi = testmeta_GP$z, 
                     vi = testmeta_GP$Variance, 
                     data = testmeta_GP)


funnel(meta_analysis_EffectSize_GP, back = "white", pch = 21)
regtest(meta_analysis_EffectSize_GP)
```

```{r meta-regressions of longitudinal effects}
data_RJA <- testmeta %>%
   filter(`IJA/RJA` == "RJA")

data_IJA <- testmeta %>%
   filter(`IJA/RJA` == "IJA")

table1_IJA_age <- rma(yi = r, 
                     vi = Variance, 
                     mods = ~`Age1 (months) - JA?`, 
                     data = data_IJA)
table1_IJA_age


table1_IJA_long <- rma(yi = r, 
                     vi = Variance, 
                     mods = ~Longitudinal_Gap, 
                     data = data_IJA)
table1_IJA_long

table1_RJA_age <- rma(yi = r, 
                     vi = Variance, 
                     mods = ~`Age1 (months) - JA?`, 
                     data = data_RJA)
table1_RJA_age


table1_RJA_long <- rma(yi = r, 
                     vi = Variance, 
                     mods = ~Longitudinal_Gap, 
                     data = data_RJA)
table1_RJA_long


data_gp <- filter(testmeta, `IJA/RJA` == "GP")


table1_gp_long <- rma(yi = r, 
                     vi = Variance, 
                     mods = ~Longitudinal_Gap, 
                     data = data_gp)

table1_gp_long <- rma(yi = r, 
                     vi = Variance, 
                     mods = ~Longitudinal_Gap, 
                     data = data_gp)

table1_gp_age <- rma(yi = r, 
                     vi = Variance, 
                     mods = ~`Age1 (months) - JA?`, 
                     data = data_gp)
table1_gp_age

data_long <- filter(testmeta, `Concurrent/Longitudinal` == "Longitudinal")


table1_long_age <- rma(yi = r, 
                     vi = Variance, 
                     mods = ~`Age1 (months) - JA?`, 
                     data = data_long)

table1_long_long <- rma(yi = r, 
                     vi = Variance, 
                     mods = ~Longitudinal_Gap, 
                     data = data_long)

```

```{r t-tests for ESCS vs GP}
testmeta <- xl.read.file("C:/Users/gs94051/Documents/Fall 2023/Research/JA Meta/testmeta.xlsx")

testmeta_GP_prod <- testmeta %>%
   filter(`IJA/RJA` == "GP" & `Comp/Prod` == "Prod")

testmeta_noGP_prod <- testmeta %>%
   filter(`IJA/RJA` != "GP"& `ESCS Y/N` == "Y" &  `Comp/Prod` == "Prod")

t.test(testmeta_noGP_prod$r, testmeta_GP_prod$r)
t.test(testmeta_GP_prod$r)
t.test(testmeta_noGP_prod$r)

testmeta_GP_comp <- testmeta %>%
   filter(`IJA/RJA` == "GP" & `Comp/Prod` == "Comp")

testmeta_noGP_comp <- testmeta %>%
   filter(`IJA/RJA` != "GP"& `ESCS Y/N` == "Y" &  `Comp/Prod` == "Comp")

t.test(testmeta_noGP_comp$r, testmeta_GP_comp$r)
t.test(testmeta_GP_comp$r)
t.test(testmeta_noGP_comp$r)

testmeta_GP <- testmeta %>%
   filter(`IJA/RJA` == "GP")

testmeta_noGP <- testmeta %>%
   filter(`IJA/RJA` != "GP"& `ESCS Y/N` == "Y")
t.test(testmeta_noGP$r, testmeta_GP$r)
t.test(testmeta_GP$r)
t.test(testmeta_noGP$r)

testmeta_GP_conc <- testmeta %>%
  filter(`Concurrent/Longitudinal` == "Concurrent" & `IJA/RJA` == "GP")

testmeta_noGP_conc <- testmeta %>%
  filter(`Concurrent/Longitudinal` == "Concurrent" & `IJA/RJA` != "GP" & `ESCS Y/N` == "Y")

t.test(testmeta_noGP_conc$r, testmeta_GP_conc$r)
t.test(testmeta_GP_conc$r)
t.test(testmeta_noGP_conc$r)

testmeta_GP_long <- testmeta %>%
  filter(`Concurrent/Longitudinal` == "Longitudinal" & `IJA/RJA` == "GP")

testmeta_noGP_long <- testmeta %>%
  filter(`Concurrent/Longitudinal` == "Longitudinal" & `IJA/RJA` != "GP" & `ESCS Y/N` == "Y")

t.test(testmeta_noGP_long$r, testmeta_GP_long$r)
t.test(testmeta_GP_long$r)
t.test(testmeta_noGP_long$r)
```


```{r t-test}

# Read the data from Excel
testmeta <- read_excel("/Users/cmj39767/Desktop/Meta/testmeta.xlsx")

# Function to format P values
format_p <- function(p_value) {
  if (p_value < 0.001) {
    return(sprintf("*** (P < %.3f)", p_value))
  } else if (p_value < 0.01) {
    return(sprintf("** (P < %.3f)", p_value))
  } else if (p_value < 0.05) {
    return(sprintf("* (P < %.3f)", p_value))
  } else {
    return(sprintf("(P = %.3f)", p_value))
  }
}

# data frame to store the results
results <- data.frame(Category = character(), 
                      RJA_T_Value = numeric(), 
                      IJA_T_Value = numeric(), 
                      P_Value_RJA = character(), 
                      P_Value_IJA = character(), 
                      Two_Sample_P_Value = numeric(), 
                      stringsAsFactors = FALSE)

# Loop through each category in 'Comp/Prod'
for (cp in unique(testmeta$`Comp/Prod`)) {
  # Subset data for IJA and RJA within the 'Comp/Prod'
  ija_data <- subset(testmeta, `IJA/RJA` == "IJA" & `Comp/Prod` == cp)
  rja_data <- subset(testmeta, `IJA/RJA` == "RJA" & `Comp/Prod` == cp)

  # Perform one-sample t-tests 
  if (length(ija_data$r) > 1) {
    t_test_ija <- t.test(ija_data$r)
    ija_t_value <- t_test_ija$statistic
    p_value_ija <- format_p(t_test_ija$p.value)
  } else {
    ija_t_value <- NA
    p_value_ija <- NA
  }

  if (length(rja_data$r) > 1) {
    t_test_rja <- t.test(rja_data$r)
    rja_t_value <- t_test_rja$statistic
    p_value_rja <- format_p(t_test_rja$p.value)
  } else {
    rja_t_value <- NA
    p_value_rja <- NA
  }

  # Perform a two-sample t-test between IJA and RJA 
  if (length(ija_data$r) > 1 && length(rja_data$r) > 1) {
    two_sample_test <- t.test(ija_data$r, rja_data$r)
    two_sample_p_value <- two_sample_test$p.value
  } else {
    two_sample_p_value <- NA
  }

  # results
  results <- rbind(results, data.frame(
    Category = cp,
    RJA_T_Value = rja_t_value,
    IJA_T_Value = ija_t_value,
    P_Value_RJA = p_value_rja,
    P_Value_IJA = p_value_ija,
    Two_Sample_P_Value = two_sample_p_value
  ))
}

# Repeat the loop for 'Concurrent/Longitudinal'
for (cl in unique(testmeta$`Concurrent/Longitudinal`)) {
  # Subset data for IJA and RJA within the 'Concurrent/Longitudinal'
  ija_data <- subset(testmeta, `IJA/RJA` == "IJA" & `Concurrent/Longitudinal` == cl)
  rja_data <- subset(testmeta, `IJA/RJA` == "RJA" & `Concurrent/Longitudinal` == cl)

  # Perform one-sample t-tests 
  if (length(ija_data$r) > 1) {
    t_test_ija <- t.test(ija_data$r)
    ija_t_value <- t_test_ija$statistic
    p_value_ija <- format_p(t_test_ija$p.value)
  } else {
    ija_t_value <- NA
    p_value_ija <- NA
  }

  if (length(rja_data$r) > 1) {
    t_test_rja <- t.test(rja_data$r)
    rja_t_value <- t_test_rja$statistic
    p_value_rja <- format_p(t_test_rja$p.value)
  } else {
    rja_t_value <- NA
    p_value_rja <- NA
  }

  # Perform a two-sample t-test between IJA and RJA 
  if (length(ija_data$r) > 1 && length(rja_data$r) > 1) {
    two_sample_test <- t.test(ija_data$r, rja_data$r)
    two_sample_p_value <- two_sample_test$p.value
  } else {
    two_sample_p_value <- NA
  }

  #results
  results <- rbind(results, data.frame(
    Category = cl,
    RJA_T_Value = rja_t_value,
    IJA_T_Value = ija_t_value,
    P_Value_RJA = p_value_rja,
    P_Value_IJA = p_value_ija,
    Two_Sample_P_Value = two_sample_p_value
  ))
}

# Calculate the totals for RJA_T_Value, IJA_T_Value, and Two_Sample_P_Value
total_rja_t_value <- sum(results$RJA_T_Value, na.rm = TRUE)
total_ija_t_value <- sum(results$IJA_T_Value, na.rm = TRUE)
total_two_sample_p_value <- sum(results$Two_Sample_P_Value, na.rm = TRUE)

# total results table
results <- rbind(results, data.frame(
    Category = "Total",
    RJA_T_Value = total_rja_t_value,
    IJA_T_Value = total_ija_t_value,
    P_Value_RJA = NA, 
    P_Value_IJA = NA,
    Two_Sample_P_Value = total_two_sample_p_value
))


print(results)

# Save the results to an Excel file
openxlsx::write.xlsx(results, file = "/Users/cmj39767/Desktop/results.xlsx")

```


```{r Bubble Plot}


testmeta$Longitudinal_Gap <- abs(testmeta$`Age2 (months) - vocab?` - testmeta$`Age1 (months) - JA?`)

# Categorize the Longitudinal Gap according to your specific groups
testmeta$Longitudinal_Gap_Category <- cut(testmeta$Longitudinal_Gap,
                                          breaks = c(-Inf, 5, 15, 25, 35, Inf),
                                          labels = c("0", "10", "20", "30", "40"),
                                          right = FALSE)

# Create the bubble plot
bubble_plot <- ggplot(testmeta, aes(x = `Age1 (months) - JA?`, 
                                    y = r, 
                                    size = Longitudinal_Gap_Category, 
                                    color = `IJA/RJA`)) +
  geom_point(alpha = 0.5) +
  scale_size_manual(values = c("0" = 3, "10" = 6, "20" = 9, "30" = 12, "40" = 15)) +
  theme_minimal() +
  labs(title = ,
       x = "Age of JA variable test",
       y = "Reported Effect Size",
       size = "Longitudinal Gap") +
  theme(legend.position = "right")

# Save the plot
ggsave("~/Desktop/bubble_plot.png", bubble_plot, width = 10, height = 7, dpi = 300)



```













